---
title: 'Criticality Dashboard (Hydrangea)'
output:
  flexdashboard::flex_dashboard:
    social: menu
    source_code: embed
runtime: shiny
---

```{r setup}

library(criticality)
library(flexdashboard)
library(ggplot2)
library(magrittr)
library(shinyWidgets)

# spline packages
library(caret)
library(dplyr)
# library(ggplot2)
# library(keras)
# library(magrittr)
library(metR)
library(viridis)

```

Column {.sidebar}
=======================================================================

```{r}

if (Sys.info()[1] == 'Darwin') {
  if (file.exists('/Volumes/LaCie/hydrangea')) {
    ext.dir <- '/Volumes/LaCie/hydrangea'
  } else {
    ext.dir <- '/Users/Will/Desktop/extdata'
  }
} else {
  if (file.exists('D:/hydrangea')) {
    ext.dir <- 'D:/hydrangea'
  } else {
    ext.dir <- 'C:/Users/Will/Desktop/extdata'
  }
}

textInput('ext.dir', label = 'external directory (full path)', value = ext.dir)
textInput('training.dir', label = 'training directory (folder name)', value = 'test')
textInput('facility.data', label = 'facility data (.csv file name)', value = 'b332.csv')

```

<br><b>Neural Network Metamodel</b>

```{r}

selectInput('code', label = 'code', choices = c('mcnp', 'cog (not supported)'))

selectInput('batch.size', label = 'batch size', choices = c(8192, 32, 64, 128, 245, 512, 1024, 2048, 4096))
selectInput('loss', label = 'loss function', choices = c('sse', 'mse'))
selectInput('opt.alg', label = 'optimization algorithm', choices = c('adamax', 'adadelta', 'adagrad', 'adam', 'nadam', 'rmsprop'))

textInput('layers', label = 'hidden layer architecture', value = '8192-256-256-256-256-16')
numericInput('val.split', label = 'validation split', value = 0.2, step = 0.1)
numericInput('ensemble.size', label = 'ensemble size', value = 1, step = 1)
numericInput('epochs', label = 'epochs', value = 1500, step = 250)
numericInput('learning.rate', label = 'learning rate', value = 0.00075, step = 0.00025)

materialSwitch('replot', label = 'replot')
materialSwitch('verbose', label = 'verbose')

```

<br><b>Risk Model</b>

```{r}

selectInput('dist', label = 'probability distribution', choices = c('gamma', 'gev', 'normal', 'log-normal', 'weibull'))
numericInput('keff.cutoff', label = 'keff cutoff', value = 0.9, step = 0.1)
numericInput('risk.pool', label = 'risk pool', value = 1, step = 1)
textInput('sample.size', label = 'sample size', value = '1e+04')

```

<br><p>

```{r}

div(style='display:inline-block;width:50%;text-align: center;', actionButton('build', 'Build Models'))

```

</p>

```{r}

training.dir <- reactive({
  paste0(input$ext.dir, '/', input$training.dir)
})

dataset <- reactive({
  criticality::Tabulate(
    code = input$code,
    ext.dir = input$ext.dir)
})

metamodel <- reactive({
  criticality::NN(
    batch.size = input$batch.size,
    code = input$code,
    dataset = dataset(),
    ensemble.size = input$ensemble.size,
    epochs = input$epochs,
    layers = input$layers,
    loss = input$loss,
    opt.alg = input$opt.alg,
    learning.rate = input$learning.rate,
    val.split = input$val.split,
    overwrite = FALSE,
    replot = input$replot,
    verbose = input$verbose,
    ext.dir = input$ext.dir,
    training.dir = training.dir())
})

bn <- eventReactive(input$build, {
  criticality::BN(
    dist = input$dist,
    facility.data = input$facility.data,
    ext.dir = input$ext.dir)
})

risk <- eventReactive(input$build, {

  risk <- criticality::Risk(
    bn = bn(),
    dist = input$dist,
    facility.data = input$facility.data,
    keff.cutoff = input$keff.cutoff,
    metamodel = metamodel(),
    risk.pool = input$risk.pool,
    sample.size = as.numeric(input$sample.size),
    ext.dir = input$ext.dir,
    training.dir = training.dir())
  
  risk.dir <- paste0(input$ext.dir, '/risk/', gsub('.csv', '', input$facility.data), '-', input$dist, '-', formatC(input$sample.size, format = 'e', digits = 0))

  if (input$keff.cutoff > 0) risk.dir <- paste0(risk.dir, '-', input$keff.cutoff)

  file.copy(c(paste0(training.dir(), '/model-settings.txt')), paste0(risk.dir, '/model-settings.txt'))

  return(risk)

})

```

Models
=======================================================================

Column
-----------------------------------------------------------------------

```{r}

training.data <- eventReactive(input$build, {
  if (file.exists(paste0(training.dir(), '/training-data.csv'))) training.data <- utils::read.csv(paste0(training.dir(), '/training-data.csv'), fileEncoding = 'UTF-8-BOM')
  return(training.data)
})

renderPlot({

  training.error <- training.data()$keff - training.data()$avg
  
  px <- pretty(training.data()$keff)
  py <- pretty(training.error)
  
  ggplot(as.data.frame(training.error), aes(x = training.data()$keff)) +
    theme_bw() +
    theme(text = element_text(color = 'grey30', size = 13), axis.text = element_text(size = 13), plot.title = element_text(color = 'black', size = 14, face = 'bold', hjust = 0.5)) +
    geom_point(aes(y = training.error)) +
    scale_x_continuous(breaks = px) +
    scale_y_continuous(breaks = py, limits = range(py)) +
    ggtitle('Training Data') +
    xlab('keff') +
    ylab('keff - predicted keff') +
    geom_hline(yintercept = mean(training.error), color = 'red', size = 0.7)
  
})

renderPlot({

  if (length(risk()[[1]]) <= 10) {
    px <- c(1:length(risk()[[1]])) 
  } else {
    px <- pretty(c(1:length(risk()[[1]])))
  }

  if (mean(risk()[[1]]) == 0) {
    py <- 0
  } else {
    py <- pretty(risk()[[1]])
  }
  
  ggplot(as.data.frame(risk()[[1]]), aes(x = c(1:length(risk()[[1]])))) +
    theme_bw() +
    theme(text = element_text(color = 'grey30', size = 13), axis.text = element_text(size = 13), plot.title = element_text(color = 'black', size = 14, face = 'bold', hjust = 0.5)) +
    geom_hline(yintercept = mean(risk()[[1]]), color = 'red', size = 0.7) +
    geom_point(aes(y = risk()[[1]])) +
    scale_x_continuous(breaks = px) +
    scale_y_continuous(breaks = py, limits = range(py), labels = function(x) format(x, scientific = TRUE)) +
    ggtitle('Process Criticality Accident Risk') +
    xlab('risk pool') +
    ylab('risk')
  
})

```

Plots
=======================================================================

Column
-----------------------------------------------------------------------

```{r}

training.data <- eventReactive(input$build, {
  if (file.exists(paste0(training.dir(), '/training-data.csv'))) training.data <- utils::read.csv(paste0(training.dir(), '/training-data.csv'), fileEncoding = 'UTF-8-BOM')
  return(training.data)
})

renderPlot({

  # set variables
  mass <- seq(100, 8000, 100)
  form <- c('alpha', 'puo2')
  mod <- c('mgo', 'sepiolite', 'ch2', 'h2o', 'none')
  rad <- seq(5, 47, 1)
  ref <- c('al', 'be', 'du', 'graphite', 'pb', 'mgo', 'ch2', 'ss304', 'h2o', 'none')
  thk <- seq(0, 6, 1) * 2.54
  shape <- 'sph'

  df <- expand.grid(mass, form, mod, rad, ref, thk, shape, stringsAsFactors = FALSE) %>% as.data.frame()
  names(df) <- c('mass', 'form', 'mod', 'rad', 'ref', 'thk', 'shape')

  # set Pu density (g/cc)
  pu.density <- ifelse((df$form == 'alpha'), 19.86, 11.5)

  # calculate vol (cc)
  vol <- 4/3 * pi * df$rad^3

  # fix mod, vol (cc), and rad (cm)
  df$mod[vol <= df$mass / pu.density] <- 'none'
  vol[vol <= df$mass / pu.density] <- df$mass / pu.density
  df$rad <- (3/4 * vol / pi)^(1/3)

  # fix ref and thk (cm)
  df$ref[df$thk == 0] <- 'none'
  df$thk[df$ref == 'none'] <- 0

  # set conc (g/cc)
  conc <- ifelse((vol == 0), 0, (df$mass / vol))

  # set form, vol (cc), and conc (g/cc)
  df$form <- ifelse((pu.density == 19.86), 'alpha', 'puo2')
  df$vol <- vol
  df$conc <- conc

  # one-hot encode categorical variables
  dummy <- dummyVars(~ ., data = dataset()$output[-c(9, 10)])
  df <- data.frame(stats::predict(dummy, newdata = df))

  # subset data frame
  df <- new.df <- subset(df, formalpha == 1 & refnone == 1)

  # scale data
  df$mass <- scale(df$mass, center = dataset()$training.mean[1], scale = dataset()$training.sd[1])
  df$rad <- scale(df$rad, center = dataset()$training.mean[2], scale = dataset()$training.sd[2])
  df$thk <- scale(df$thk, center = dataset()$training.mean[3], scale = dataset()$training.sd[3])
  df$vol <- scale(df$vol, center = dataset()$training.mean[4], scale = dataset()$training.sd[4])
  df$conc <- scale(df$conc, center = dataset()$training.mean[5], scale = dataset()$training.sd[5])

  # convert data frame to matrix (Keras requirement)
  df <- as.matrix(df)

  keff <- matrix(nrow = nrow(df), ncol = input$ensemble.size)

  # for (i in 1:input$ensemble.size) {
  #   keff[ , i] <- metamodel()[[1]][[i]] %>% predict(df)
  # }
  
  keff[ , 1] <- metamodel()[[1]][[1]] %>% predict(df)
  
  new.df$keff <- rowMeans(keff)
  
  ggplot(subset(new.df, modh2o == 1) %>% unique(), aes(x = rad, y = mass, z = keff)) +
    theme_bw() +
    theme(text = element_text(color = 'grey30', size = 13), axis.text = element_text(size = 13), plot.title = element_text(color = 'black', size = 14, face = 'bold', hjust = 0.5)) +
    geom_contour_filled(aes(z = keff), alpha = 0.7, linetype = 'solid') +
    geom_text_contour(aes(z = keff), color = 'grey30', size = 4.5) +
    scale_fill_viridis(option = 'mako', discrete = TRUE) +
    scale_x_continuous(limits = c(5, 47), expand = c(0, 0)) +
    scale_y_continuous(limits = c(100, 4000), expand = c(0, 0)) +
    theme(legend.position = 'none',
          panel.grid = element_blank(),
          panel.border = element_blank()) +
    ggtitle('keff Contour Plot') +
    xlab('radius (cm)') +
    ylab('plutonium mass (g)')
  
})

```

References
=======================================================================

Column
-----------------------------------------------------------------------

<b>Software Packages</b>

bnlearn: An R package for Bayesian Network Learning and Inference<br>
[https://www.bnlearn.com/](https://www.bnlearn.com/)

criticality: Modeling Fissile Material Operations in Nuclear Facilities<br>
[https://github.com/willzywiec/criticality](https://github.com/willzywiec/criticality)

hydrangea: Dashboard for the criticality Software Package<br>
[https://github.com/willzywiec/hydrangea](https://github.com/willzywiec/hydrangea)

<b>Papers and Presentations</b>

Analysis of Process Criticality Accident Risk Using a Metamodel-Driven Bayesian Network<br>
[https://github.com/willzywiec/dissertation](https://github.com/willzywiec/dissertation)
[https://www.sciencedirect.com/science/article/abs/pii/S0951832020308152](https://www.sciencedirect.com/science/article/abs/pii/S0951832020308152)
